Financialisation of commodities: co-movement behind-the-scenes

### 2021-09-01 docs/paper.Rmd
github pages

---
title: 'Financialisation of commodities: co-movement behind-the-scenes'
subtitle: "A tale of four factors"
date: "`r format(Sys.Date(), '%B %Y')`"
abstract: |
  The last two decades have seen major changes in the nature of the commodity markets with the influx of financial investor inflows followed by the financial crisis. We study the effects of these events on commodity futures pricing dynamics using commodity asset pricing techniques. We find that Keynesian and Working’s term structure paradigms based factors are best able to detect the effects of commodity financialisation, while the effects of the financial crisis and its aftermath are most clearly visible through the performance of the market factor. Besides, the effects of financialisation seem to go beyond mechanical effects induced by the rise of indexing.
bibliography: literature_files/references.bib
output:
  bookdown::gitbook:
    pandoc_args: html.yaml
    split_by: "chapter"
    css: style.css
    toc_depth: 3
    config:
      toc:
        collapse: subsection
        scroll_highlight: true
        before: |
          <li><a href="index.html">Financialization: co-movement</a></li>
      edit: https://github.com/bautheac/financialisation-co-movement/edit/master/%s
      sharing:
        facebook: true
        twitter: true
        whatsapp: true
        all: ['whatsapp', 'twitter', 'facebook']
      download: [ ["paper.pdf", "pdf"] ]
      info: false
    includes:
      after_body: doc_suffix.html
  bookdown::pdf_book:
      pandoc_args: latex.yaml
      base_format: rticles::elsevier_article
      latex_engine: xelatex
      toc_depth: 3
      includes:
        in_header: preamble.tex
---

>>>>

---
title: 'Financialisation of commodities: co-movement behind-the-scenes'
subtitle: "A tale of four factors"
date: "`r format(Sys.Date(), '%B %Y')`"
abstract: |
  The last two decades have seen major changes in the nature of the commodity markets with the influx of financial investor inflows followed by the financial crisis. We study the effects of these events on commodity futures pricing dynamics using commodity asset pricing techniques. We find that Keynesian and Working’s term structure paradigms based factors are best able to detect the effects of commodity financialisation, while the effects of the financial crisis and its aftermath are most clearly visible through the performance of the market factor. Besides, the effects of financialisation seem to go beyond mechanical effects induced by the rise of indexing.
bibliography: literature_files/references.bib
github-repo: bautheac/financialisation-co-movement
output:
  bookdown::gitbook:
    pandoc_args: html.yaml
    split_by: "chapter"
    css: style.css
    toc_depth: 3
    config:
      toc:
        collapse: subsection
        scroll_highlight: true
        before: |
          <li><a href="index.html">Financialization: co-movement</a></li>
        after: |
          <li id="github"><a href="https://github.com/bautheac/financialisation-co-movement"><img src="github.png" alt="github" width="50" height="50"></a></li>
      sharing:
        facebook: true
        twitter: true
        whatsapp: true
        all: ['whatsapp', 'twitter', 'facebook']
      download: [ ["paper.pdf", "pdf"] ]
      info: false
    includes:
      after_body: doc_suffix.html
  bookdown::pdf_book:
      pandoc_args: latex.yaml
      base_format: rticles::elsevier_article
      latex_engine: xelatex
      toc_depth: 3
      includes:
        in_header: preamble.tex
---
